---
title: "Chocolate analysis"
author: "Silvia Cicconi"
date: '2022-03-17'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
devtools::load_all(".")
```

```{r load data}
choc <- read.csv(here::here("analysis/data/raw_data/Chocolate.csv"))
```

This dataset comes from Flavors of Cacao and was used for an analysis in 2017 at Kaggle. Data are available in tydyverse https://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-01-18/readme.md

```{r number of observations, echo=FALSE}
n <- nrow(choc)
year_min <- min(choc$review_date)
year_max <- max(choc$review_date)
```

The dataset contains `r n` ratings of chocolate from `r year_min` to `r year_max`. The following variables are provided: 

```{r var_names, echo=FALSE}
names(choc)
```

The bar chart below shows the distribution of ratings over time. 

```{r ratings_years, echo=FALSE}
barplot(table(choc$review_date), ylim=c(0, 300), las=2, ylab="No. ratings", xlab="Years")
```


Ratings were given on a scale from 1 to 10. The chocolate ratings by cocoa percentage are presented below for companies located in Switzerland.

```{r tab_swiss_rating_cocoaperc, echo=FALSE}
tab(choc$rating[which(choc$company_location=="Switzerland")], choc$cocoa_percent[which(choc$company_location=="Switzerland")])
```





